Performance Evaluation of Big Data Processing Strategies for Neuroimaging

### 2018-12-14 paper.tex

@@

>>>>

It was expected that Spark would experience longer processing times, particularly
with the small datasets, due to Java serializing. This was not found to be the case. 
Unlike Spark, Nipype performs a more thorough provenance capture, potentially owing to longer
processing times.

@@

Big Data performance optimization strategies help improve performance of typical 
neuroimaging applications. Our experiments indicate that overall, in-memory computing 
enables greater speedups than what can be obtained by using page cache and tmpfs. 
While page cache and tmpfs do give memory-like performance, they are likely to fill
up faster than memory, leading to increased performance penalties when compared
to in-memory computing.

Data-locality was also found to play an important role in 
application performance. Local disk was found to perform between than the shared
filesystem, despite having lower bandwidth, due to increased contention on the 
shared filesystem. As local disk will generally have less contention than a 
shared filesystem. It is recommended to have the data stored locally. Although, 
storing data locally may come at a cost to fault tolerance.

Although a more thorough analysis of lazy evaluation remains to be performed, it
is speculated that this may be the cause of the general performance difference 
between Spark and Nipype. Furthermore, it is found that lazy evaluation optimizations increase 
the likelihood of cache hits, thus improving overall performance.

Even though Big Data strategies are beneficial to the processing of Big 
neuroimaging data, it is estimated that it would require running a functional MRI
dataset with 200 concurrent subjects for any noticeable impact using our Lustre 
bandwidth estimate.

To further improve neuroimaging data processing times, scheduling strategies for 
Big Data application in a multitenant environment need to be investigated. 
Additionally, workflow-aware cache eviction policies that maximizes page cache 
usage for the workflows should be investigated.
